Modelling and Analysis of an Interventional X-Ray System with NuSMV2

### 2013-07-03 paper/main.tex
paper: Added LTL formulas and corrected some typos

% Math
\newcommand{\LTLG}{\mathbf{G~}}
\newcommand{\LTLF}{\mathbf{F~}}
\newcommand{\LTLX}{\mathbf{X~}}
\newcommand{\LTLU}{\mathbf{~U~}}
\newcommand{\LTLO}{\mathbf{O~}}
\newcommand{\LTLY}{\mathbf{Y~}}
\newcommand{\LTLH}{\mathbf{H~}}
\newcommand{\LTLS}{\mathbf{~S~}}
\newcommand{\disjall}[2]{\mathop{\bigvee}\limits_{#1}^{#2}}
\newcommand{\conjall}[2]{\mathop{\bigwedge}\limits_{#1}^{#2}}
\newcommand{\imply}{\rightarrow}
\newcommand{\doselow}{\textrm{dose\_low}}
\newcommand{\doseno}{\textrm{dose\_no}}
\newcommand{\dosehigh}{\textrm{dose\_high}}
\newcommand{\dosehighseq}{\textrm{dose\_highseq}}
\newcommand{\dosehighone}{\textrm{dose\_highone}}
\newcommand{\lowsignal}{\textrm{low\_signal}}
\newcommand{\highsignal}{\textrm{high\_signal}}
\newcommand{\errorany}{\textrm{error\_any}}
\newcommand{\errorhigh}{\textrm{error\_high}}
\newcommand{\lowmode}{\textrm{low\_mode}}

@@

		\item \textbf{The system is not prepared or a dose is started if there is an error for the corresponding type and Xplane.}
			\begin{align*}
				\LTLG &(!\textrm{o.prepared} \land \errorhigh \land (\LTLF !\errorhigh) \imply (!\textrm{o.prepared} \LTLU !\errorhigh)) \land \\
						& %TODO
			\end{align*}

		\item \textbf{For Low dose a degraded mode is used in case of an error, that is, if Xplane Both is requested then}
			\begin{enumerate}
				\item only Xplane Front is used if SideLowError holds;
					\[
					\hspace{-8em}	(\LTLG !\errorhigh) \imply \LTLG (\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.FrontLowError} \land (!\LTLF \textrm{e.FrontLowError}) \imply \LTLF \textrm{o.direction = Side})
					\]
				\item only Xplane Side is used if FrontLowError holds.
					\[
					\hspace{-8em}	(\LTLG !\errorhigh) \imply \LTLG (\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.SideLowError} \land (!\LTLF \textrm{e.SideLowError}) \imply \LTLF \textrm{o.direction = Front})
					\]
			\end{enumerate}

@@

@@

			The last remark is in conflict with that HighFront should still function in case of a HighSideError.
			Thus it is disregarded.

@@

	\section{Reflection}
	We had some troubles while making this assignment.
	The most difficult part was dealing with the requirements sheet.
	The requirements are not exhaustive, some are ambiguious and some are simply vague.
	This is partly due to that the system itself is very complicated and in some situations counter-intuitive.
	The videos help a bit, but also do not cover all possible situations.
	It would have been helpful to have some sort of black box to test situations on.
	If this would have been a real world scenario, there would naturally not be a black box available.

>>>>

% Math
\newcommand{\LTLG}{\mathbf{G~}}
\newcommand{\LTLF}{\mathbf{F~}}
\newcommand{\LTLX}{\mathbf{X~}}
\newcommand{\LTLU}{\mathbf{~U~}}
\newcommand{\LTLO}{\mathbf{O~}}
\newcommand{\LTLY}{\mathbf{Y~}}
\newcommand{\LTLH}{\mathbf{H~}}
\newcommand{\LTLS}{\mathbf{~S~}}
\newcommand{\disjall}[2]{\mathop{\bigvee}\limits_{#1}^{#2}}
\newcommand{\conjall}[2]{\mathop{\bigwedge}\limits_{#1}^{#2}}
\newcommand{\imply}{\rightarrow}
\newcommand{\doselow}{\textrm{dose\_low}}
\newcommand{\doseno}{\textrm{dose\_no}}
\newcommand{\dosehigh}{\textrm{dose\_high}}
\newcommand{\dosehighseq}{\textrm{dose\_highseq}}
\newcommand{\dosehighone}{\textrm{dose\_highone}}
\newcommand{\lowsignal}{\textrm{low\_signal}}
\newcommand{\highsignal}{\textrm{high\_signal}}
\newcommand{\errorany}{\textrm{error\_any}}
\newcommand{\errorlow}{\textrm{error\_low}}
\newcommand{\errorlowboth}{\textrm{error\_lowboth}}
\newcommand{\errorhigh}{\textrm{error\_high}}
\newcommand{\lowmode}{\textrm{low\_mode}}

@@

		\item \textbf{The system is not prepared or a dose is started if there is an error for the corresponding type and Xplane.} %TODO KLOPT NOG NIET?
			\begin{align*}
				\LTLG &(!\textrm{o.prepared} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!\textrm{o.prepared} \LTLU !\errorhigh)) \land \\
				& (\doseno \land \textrm{i.signal = LowFrontOn} \land \textrm{e.FrontLowError} \land (\LTLF !\textrm{e.FrontLowError}) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Front} \land \doselow) \LTLU !\textrm{e.FrontLowError})) \land \\
				& (\doseno \land \textrm{i.signal = LowSideOn} \land \textrm{e.SideLowError} \land (\LTLF !\textrm{e.SideLowError}) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Side} \land \doselow) \LTLU !\textrm{e.SideLowError})) \land \\
				& (\doseno \land \textrm{i.signal = LowBothOn} \land \errorlow \land (\LTLF !\errorlow) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Both} \land \doselow) \LTLU !\errorlow)) \land \\
				& (\textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Front} \land \textrm{e.FrontHighError} \land (\LTLF !\textrm{e.FrontHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighseq \land \textrm{o.direction = Front}) \LTLU !\textrm{e.FrontHighError})) \land \\
				& (\textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Side} \land \textrm{e.SideHighError} \land (\LTLF !\textrm{e.SideHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighseq \land \textrm{o.direction = Side}) \LTLU !\textrm{e.SideHighError})) \land \\
				& (\textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Both} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!(\dosehighseq \land \textrm{o.direction = Both}) \LTLU !\errorhigh)) \land \\
				& (\textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Front} \land \textrm{e.FrontHighError} \land (\LTLF !\textrm{e.FrontHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighone \land \textrm{o.direction = Front}) \LTLU !\textrm{e.FrontHighError})) \land \\
				& (\textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Side} \land \textrm{e.SideHighError} \land (\LTLF !\textrm{e.SideHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighone \land \textrm{o.direction = Side}) \LTLU !\textrm{e.SideHighError})) \land \\
				& (\textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Both} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!(\dosehighone \land \textrm{o.direction = Both}) \LTLU !\errorhigh))
			\end{align*}
		\item \textbf{For Low dose a degraded mode is used in case of an error, that is, if Xplane Both is requested then}
			\begin{enumerate}
				\item only Xplane Front is used if SideLowError holds;
					\begin{align*}
						(\LTLG !\errorhigh) \imply \LTLG &(\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.FrontLowError} \land (!\LTLF \textrm{e.FrontLowError}) \\
						&\hspace{1em}	\imply \LTLF \textrm{o.direction = Side})
					\end{align*}
				\item only Xplane Side is used if FrontLowError holds.
					\begin{align*}
						(\LTLG !\errorhigh) \imply \LTLG &(\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.SideLowError} \land (!\LTLF \textrm{e.SideLowError}) \\
						&\hspace{1em}	\imply \LTLF \textrm{o.direction = Front})
					\end{align*}
			\end{enumerate}

@@

			\begin{align*}
				\LTLG & (\textrm{e.FrontLowError} \land \textrm{i.signal = LowFrontOn} \imply \LTLF !(\textrm{o.direction = Front} \land \doselow)) \land \\
				& (\textrm{e.SideLowError} \land \textrm{i.signal = LowSideOn} \imply \LTLF !(\textrm{o.direction = Side} \land \doselow)) \land \\
				& (\errorlowboth \land \textrm{i.signal = LowBothOn} \imply \LTLF !\doselow) \land \\
				& (\textrm{e.FrontHighError} \land \textrm{next\_direction = Front} \land \textrm{i.signal} \in \{\textrm{StartSeqHigh, StartOneHigh}\} \\
				&\hspace{1em}	\imply \LTLF !(\textrm{o.direction = Front} \land \dosehigh)) \land \\
				& (\textrm{e.SideHighError} \land \textrm{next\_direction = Side} \land \textrm{i.signal} \in \{\textrm{StartSeqHigh, StartOneHigh}\} \\
				&\hspace{1em}	\imply \LTLF !(\textrm{o.direction = Side} \land \dosehigh)) \land \\
				& (\errorhigh \land \textrm{next\_direction = Both} \land \textrm{i.signal} \in \{\textrm{StartSeqHigh, StartOneHigh}\} \imply \LTLF !\dosehigh)
			\end{align*}

@@

			\begin{align*}
				\LTLG & (\doselow \land \textrm{o.direction} \in \{\textrm{Front, DegradedFront}\} \land \textrm{e.FrontLowError} \imply \LTLF !\doselow) \land \\
				&  (\doselow \land \textrm{o.direction} \in \{\textrm{Side, DegradedSide}\} \land \textrm{e.FrontSideError} \imply \LTLF !\doselow) \land \\
				& (\doselow \land \textrm{o.direction = Both} \land \errorlow \imply \LTLF !\doselow)
			\end{align*}

			The last remark is in conflict with that HighFront should still function in case of a HighSideError.
			Thus it is disregarded. Also for high doses, this requirement is basically the same as requirement number 12.

@@

	\section{Reflection}
	We had some troubles while making this assignment.
	The most difficult part was dealing with the requirements sheet.
	The requirements are not exhaustive, some are ambiguous and some are simply vague.
	This is partly due to that the system itself is very complicated and in some situations counter-intuitive.
	The videos help a bit, but also do not cover all possible situations.
	It would have been useful to have some sort of black box to test situations on.
	Although if this would have been a real world scenario, there would naturally not be a black box available either.
	Another issue was that we did not have enough time in the end to pay a lot of attention to this report, for instance.
